---
title: "HW3-MATH4322"
author: "Anthony Castillo ID:1670011"
date: "2022-10-02"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1 (a):\
$\hat{y} = -6+0.05*hours+1*undergrad GPA+ \epsilon$\
if hours = 40 & undergrad GPA = 3.5 so,\
$\hat{y} = -6 + 0.05*40+1*3.5$\
```{r}
prob<- exp(-6+(0.05*40)+(1*3.5))
q1<-prob/(1+prob)
q1
```

Question 1 (b):\
p(X)=.5\
log(P(X)/1-P(X)) = b0+b1*x1
```{r}
log(.5/(1-.5))
```

0 = -2.5+0.05*hours\
2.5/0.05 = 50\
The amount of hours needed to study to achieve an A is 50 hours\
Question 2 (a):\
```{r}
library(ISLR)
newAuto <- data.frame(Auto)
mpg.med <- median(Auto$mpg)
newAuto$mpg01 <- ifelse(Auto$mpg > mpg.med, yes = 1,no=0)
```
Question 2 (b):\
```{r}
pairs(newAuto)
par(mfrow=c(2,2))
boxplot(newAuto$mpg~newAuto$mpg01)
boxplot(newAuto$cylinders~newAuto$mpg01)
boxplot(newAuto$displacement~newAuto$mpg01)
boxplot(newAuto$horsepower~newAuto$mpg01)
boxplot(newAuto$weight~newAuto$mpg01)
boxplot(newAuto$acceleration~newAuto$mpg01)
boxplot(newAuto$year~newAuto$mpg01)
boxplot(newAuto$origin~newAuto$mpg01)
```

The best predictors seem to be the variable cylinders, displacement, horsepower, and weight\
Question 2 (c):\
```{r}
set.seed(1)
n <- nrow(newAuto)
train <- sample(1:n,0.7*n)
auto.train <- newAuto[train,]
auto.test <- newAuto[-train,]
```
Question 2 (d):\
```{r}
auto.glm <- glm(mpg01~cylinders+displacement+horsepower+weight,data =  newAuto, family = "binomial")
#summary(auto.glm)
glm.pred <- predict.glm(auto.glm,newdata = auto.test,type = "response")
yhat <- glm.pred > 0.5
table(auto.test$mpg01,yhat)
mean(yhat!=auto.test$mpg01)
```
The test error rate is (3+6)/(51+58+6+3) = 0.07627119\
Question 3 (a):\
```{r}
Power<- function(x=2,a=3){
  result <- x^a
  print(result)
}
Power()
```
Question 3 (b):\
```{r}
Power2 <- function(x,a){
  result <-x^a
  print(result)
}
Power2(3,8)
```


Question 3 (c):\
```{r}
Power2(10,3)
Power2(8,17)
Power2(131,3)
```

Question 3 (d):\
```{r}
Power3 <- function(x,a){
  result <- x^a
  return(result)
}
```
Question 3 (e):\
```{r}
x <- 1:10
plot(x,Power3(x,2),main="f(x)=x^2",ylab = "f(x)",xlab="x")

```

Question 3 (f):\
```{r}
PlotPower <- function(x,a){
  x<-seq(min(x),max(x))
  plot(x,Power3(x,a),main = "x against x^a",ylab = "f(x)",xlab = "x")
}
PlotPower(1:10,3)
```

